An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-25 EconGrowth.Rnw
Now creating graphs of lambda and alpha as a function of gamma for ZA Cobb-Douglas wtih energy.

seFromNlsModel <- function(model) { 
  return(summary(model)$sigma)
}

gammaGrid <- seq(0.05, 0.95, by=0.1)
models <- cdGrid("US", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
data <- cbind(gammaGrid, SSE)
print("US")
plot(gammaGrid, SSE)
print(coef(models[[2]]))

models <- cdGrid("ZA", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
data <- cbind(gammaGrid, SSE)
print("ZA")
plot(gammaGrid, SSE)
print(coef(models[[5]]))

>>>>

print("US")
gammaGrid <- seq(0.05, 0.95, by=0.1)
models <- cdGrid("US", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
data <- cbind(gammaGrid, SSE)
plot(gammaGrid, SSE)
print(coef(models[[2]]))

print("ZA")
models <- cdGrid("ZA", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
print(str(coef(models[[5]])))
lambda <- lapply(models, function(model) coef(model)["lambda"])
alpha <- lapply(models, function(model) coef(model)["alpha"])
data <- cbind(gammaGrid, lambda, alpha, SSE)
plot(gammaGrid, SSE)
plot(gammaGrid, lambda)
plot(gammaGrid, alpha)
print(coef(models[[5]]))
